### 2019-03-12 paper/sex_selection_spacing-ver2.tex
Discuss middle education results

The previous literature finds that women with no education are the least likely to use 
sex selection, which suggests that they would instead follow a traditional strategy to son 
preference with higher fertility and shorter birth intervals the fewer sons they have.
This pattern is supported by Figure \ref{fig:bootstrap_low}, but with important
differences across spells.
Most of the women without education live in rural areas, and I therefore focus on rural 
women.

@@

Women with one to seven years of education follow a pattern
broadly similar to those with no education as 
Figure \ref{fig:bootstrap_med} shows.
The sample size is more evenly distributed across urban and rural 
for this education group than for the no education women.
As a result, the only spells where there are few women to base 
results on are for the fourth spell for urban women and the first 
period of the fourth spell for rural women.

The spacing between births increased over the four decades.
On average, the increase is approximately three to four months.
The exception is again the first spell, where the time from
marriage to first birth remained the same or fell slightly.

In the period before sex selection became available, 1972--1985,
the differences in spacing between only girls and only boys
increase with between the second and third spell.
For both urban and rural women, the difference in duration is just over
a month for the second spell, but it is 1.4 and 2.8 months for urban and
rural women, respectively, for the third spell.
In the three later periods, there is no clear pattern
in the differences across sex compositions.

The differences in duration between only girls and only boys 
appear to decrease over time.
The exception is for the two later periods where the
differences are slightly larger in the last period compared
with the second-to-last period.

The decreases in differences are accompanied by increases
in predicted sex ratios, some of which are statistically 
significantly different from the natural sex ratio.
Hence, even though the evidence is not substantial, it does
appear that women with one to seven years of education 
have begun to use sex selection at higher-order spells.

>>>>

The previous literature finds that women with no education are the least likely to use 
sex selection, which suggests that they would instead follow a traditional strategy to son 
preference with higher fertility and shorter birth intervals the fewer sons they have.
This pattern is supported by Figure \ref{fig:bootstrap_low}, but with important
differences across spells.
Most of the women without education live in rural areas, and I therefore focus on rural 
women.%
\footnote{
Only between ten and twenty percent of the surveyed women without education live in urban 
areas, and this proportion has been decreasing over time.
}

@@

Figure \ref{fig:bootstrap_med} shows that women with one to seven years of education 
follow a fertility pattern broadly similar to those with no education.
As expected, fertility is lower than for women with no education, but still show
substantial son preference in the parity progression behavior.
Except for the second spell, the likelihood of having a birth by the end of spell is
substantially lower if there has been at least one male birth than if there are only girls.
Despite this, the probability of a birth in the third and fourth spells has also been 
falling for those with only girls.
Having a second birth is still close to universal, although in urban areas it is down to
just over 85 percent for those with a son as their first child.

The spacing between births has increased over the four decades, and the increases are 
larger than for women without any education across all spells.
Contrary to women without education, however, there has not been an increased divergence 
in birth intervals lengths across sex compositions for the third and fourth spells.
On the contrary, for the third spell the largest increases in birth intervals are for women with
two daughters and no sons, with an increase of about seven months across the four decades.
The results is that for urban women the standard spacing pattern reversed, so the longest 
predicted spacing is now for those with only girls, while for rural women the predicted 
average birth intervals are now almost identical across sex compositions of prior children.
For the fourth spell, the increases in spacing for women with only girls have kept pace
with the other sex compositions in rural areas.%
\footnote{
Because of low number of observations the pattern for the fourth spell is more noisy for 
urban women.
}

The substantial increases in spacing for women with only girls is not evidence of lower
son preference as the changes in the predicted sex ratios show.
For both the third and fourth spell the predicted sex ratio in both urban and rural
areas is statistically significantly above the natural sex ratio at between 55.5 and 57.7 
percent boys.
The elevated sex ratios strongly suggests that sex selection is driving the increases in
birth intervals for women with only girls, and that without sex selection we would 
instead have observed a diverging pattern in birth intervals across sex composition as
for women without education.
